Block bootstrap consistency\\under weak assumptions

### 2015-12-31 Paper.tex
[#5] Fix typo in Lemma 1
This commit fixes a typo pointed out by one of the referees.
Closes #5

\begin{lem}\label{block-length-convergence-lemma}
  Suppose that $M_{n1}, M_{n2},\dots$ are i.i.d.\ geometric random
  variables with success parameter $p_n = c n^{-a}$ with $a, c \in
  (0,1)$, and that $\ell_n = (p_n \log p_n^{-1})^{-1}$ and define
  $J_n$ so that $\sum_{i=1}^{J_n-1} < n \leq \sum_{i=1}^{J_n} M_{ni} $
  Then
  \begin{enumerate}
  \item $\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} / n \to^p 0$
    for any positive $C$,
  \item $\max_{i=1,\dots,J_n} M_{ni} / n \to^p 0$,
  \item $\max_{i=1,\dots,  \lfloor C n p_n \rfloor} M_{ni} /
  \ell_n^{1+\epsilon} \to^p 0$ as $n \to \infty$ for any positive
  $\epsilon$ and $C$,
  \item $\max_{i=1,\dots,J_n} M_{ni} /
  \ell_n^{1+\epsilon} \to^p 0$ as $n \to \infty$ for any positive
  $\epsilon$, and
  \item $\sum_{i=1}^{J_n} M_{ni}^2 / n^2 \to^p 0$.
  \end{enumerate}
\end{lem}

>>>>

\begin{lem}\label{block-length-convergence-lemma}
  Suppose that $M_{n1}, M_{n2},\dots$ are i.i.d.\ geometric random
  variables with success parameter $p_n = c n^{-a}$ with $a, c \in
  (0,1)$, and that $\ell_n = (p_n \log p_n^{-1})^{-1}$ and define
  $J_n$ so that $\sum_{i=1}^{J_n-1} M_{ni} < n \leq \sum_{i=1}^{J_n} M_{ni} $
  Then
  \begin{enumerate}
  \item $\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} / n \to^p 0$
    for any positive $C$,
  \item $\max_{i=1,\dots,J_n} M_{ni} / n \to^p 0$,
  \item $\max_{i=1,\dots,  \lfloor C n p_n \rfloor} M_{ni} /
  \ell_n^{1+\epsilon} \to^p 0$ as $n \to \infty$ for any positive
  $\epsilon$ and $C$,
  \item $\max_{i=1,\dots,J_n} M_{ni} /
  \ell_n^{1+\epsilon} \to^p 0$ as $n \to \infty$ for any positive
  $\epsilon$, and
  \item $\sum_{i=1}^{J_n} M_{ni}^2 / n^2 \to^p 0$.
  \end{enumerate}
\end{lem}
